---
title: "Homework 6 solutions"
author: "Tianheng Hu"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


```{r load_libraries}
library(tidyverse)
library(modelr)
library(p8105.datasets)
```

### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Problem 2

Load and tidy the datasets.
```{r}
baby_df = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(babysex= as.factor(babysex),
         frace= as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace)) %>% 
  drop_na()
```

The birthweight dataset contains `r nrow(baby_df)` rows and `r ncol(baby_df)` columns. 


fit a model

```{r}
model_fit = lm(bwt ~ ., data = baby_df)
step.model <- step(model_fit, direction = "both", 
                      trace = FALSE)
summary(step.model)
```

I used stepwise selection method to choose an appropriate model. The selection leaves me babysex, bhead , blength, delwt, fincome, gaweeks, mheight, mrace, parity, ppwt and smoken as significant predictors. 

Use those final predictors to run a final regression model.
```{r}
final_mod = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = baby_df) 

final_mod %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

```{r}
baby_df %>% 
  modelr::add_residuals(final_mod) %>% 
  modelr::add_predictions(final_mod) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()  +
labs(title = "Model residuals against Fitted values", 
    x = "Fitted Value",
     y = "Residuals")
```

The residuals are randomly scattered around y = 0. Therefore, the model is an appropriate model for this birthweight data. 


Compare model with the other two using cross validation.

```{r}
cv_df = 
  crossv_mc(baby_df, 100) 

cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    final_mod  = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
    mod1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod2  = map(train, ~lm(bwt ~ bhead +  blength + babysex + babysex * blength + babysex * bhead + blength * bhead + babysex * blength * bhead, data = .x))) %>% 
  mutate(
    rmse_final = map2_dbl(final_mod, test, ~rmse(model = .x, data = .y)),
    rmse1 = map2_dbl(mod1, test, ~rmse(model = .x, data = .y)),
    rmse2 = map2_dbl(mod2, test, ~rmse(model = .x, data = .y))) 

```




Make a plot to compare rmse for three models.
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```


From the plot above, the final model that I built has the lowest mean rmse. Therefore, this model is the best.



